EIP CRE transmission network manuscript figures and data

### 2022-09-13 manuscript-figures.Rmd
Add supplementary file

>>>>

## Supplemental file with isolate IDs and information

```{r}
sample_metadat <- read_csv('data/eip-metadat-short.csv') %>% 
  rename(Pat_ID = Patient_ID) %>% 
  mutate(Species = gsub('cloacae', 'hormaechei', Species),
         ST = gsub('cloacae', 'hormaechei', ST)) %>% 
  left_join(facil_st) %>% 
  select(-c(latitude, longitude))

all_sample_info_not_tn <- sample_metadat %>% 
  select(Fac_ID, Facility_ID) %>% 
  filter(!is.na(Facility_ID)) %>% 
  unique() %>% 
  right_join(sample_metadat %>% select(-Facility_ID)) %>% 
  select(-Patient_ID) %>% 
  left_join(sample_metadat %>% 
              select(Pat_ID, Patient_ID) %>% 
              filter(!is.na(Patient_ID)) %>% 
              unique()) %>% 
  mutate(Cult_Year = gsub('-.*', '', Cult_Date)) %>% 
  filter(State != 'TN') %>% 
  arrange(Patient_ID) %>% 
  mutate(Pat_ID = factor(Pat_ID, levels = unique(Pat_ID)),
         Patient_ID = ifelse(is.na(Patient_ID), paste0('P', as.numeric(factor(Pat_ID))), Patient_ID),
         Patient_ID = ifelse(Patient_ID == 'PNA', NA, Patient_ID)) %>% 
  select(Sample_ID, Patient_ID, Facility_ID, Cult_Year, State, Species, ST) %>% 
  arrange(Sample_ID)

all_sample_info_not_tn %>% 
  write_csv('data/supp_file_1.csv')
```
